---
title: "HW3-ESM 204"
author: "Kira Archipov, Stephanie Luu, Leah Makler"
date: "2023-05-17"
output: 
  html_document:
    code_folding: hide
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message= FALSE, warning=FALSE, results=FALSE)
library(tidyverse)
library(here)
library(ggpubr)
library(janitor)
library(broom)
library(knitr)
library(car)
library(dplyr)
library(pracma)
```

Question 1: 
```{r}
ev_data <- read_csv(here("data/HW3_data.csv")) %>% 
  clean_names()

ev_longer <- ev_data %>% 
  pivot_longer(cols = !price_dollars, 
               names_to = "consumer_type",
               values_to = "quantity") %>% 
  group_by(consumer_type)

dac_demand_model <- lm(price_dollars~q_dac, ev_data)

non_dac_demand_model <-lm(price_dollars~q_non_dac, ev_data)

dac_demand_func <- function(Q){
  P= 116854.836-6.611*Q
}
nondac_demand_func <- function(Q){
  P=  158034.280-2.731*Q
}

ggplot(data = ev_longer, aes(x = quantity, y = price_dollars, color = consumer_type)) + 
  geom_point() + 
  ylim(0, 190000) +
  xlim(0, 90000) +
  stat_function(fun = function(Q) dac_demand_func(Q)) +
  stat_function(fun = function(Q) nondac_demand_func(Q)) + 
  stat_function(fun = function(Q) agg_demand_func(Q)) +
  theme_minimal() 

```

```{r}
equatiomatic::extract_eq(dac_demand_model, use_coefs = TRUE)

equatiomatic::extract_eq(non_dac_demand_model, use_coefs = TRUE)
```

Answer Q's here

Question 2:
```{r}
300*63

external_cost<- function(V){
  C = 18900*V
}


```
MEC: P=$18,900*Q
 
 Question 3:
 
```{r}
#agg demand
dac_demand_func_p <- function(P){
  Q= 21767.635-(P/6.611)
}
nondac_demand_func_p <- function(P){
  Q=69587.85-(P/2.731)
}

agg_demand_func_p <- function(P){
  Q=91355.485-0.5174*P
  return(Q)
}

#in terms of q
agg_demand_func <- function(Q){
  P=176566.45-(Q/.5174)
}

q1<-agg_demand_func_p(50000)

slope <- 50000/q1

private_cost <- function(Q){
  P=0.763528*Q
}

#ggplot()
```
 Answers:
 
 agg demand function:  P=176566.45-(Q/.5174)
 
 supply function (MPC): P = .763528*Q
 
```{r}
#calculating social cost function
social_cost <- function(Q){
  P= external_cost(Q) + private_cost(Q)
}

social_diff<- function(Q){
   Z= social_cost(Q)-agg_demand_func(Q)
   return(Z)
}


q_msc <- fzero(social_diff, c(0,1000))$x
q_msc


private_diff<- function(Q){
   Z= private_cost(Q)-agg_demand_func(Q)
   return(Z)
}

q_mpc <- fzero(private_diff, c(0,1000000))$x
q_mpc

delta_q <- q_mpc-q_msc # height of triangle

p1 <- social_cost(65485.48)
p0 <- private_cost(65485.48)

delta_p <- p1-p0

env_cost<- delta_q*delta_p*.5 #triangle = dead weight loss

p1_b<- social_cost(9.34)
p0_b<- private_cost(9.34)

delta_p_b <- p1_b-p0_b

benefit <- delta_p_b*q_msc

benefit_cp <- benefit/2 #benefit to consumers and producers is the same
```
 
 benefit to consumers: 824447.7
 
 benefit to producers: 824447.7
 
 environmental cost at status quo: 4.051911e+13
 
 
Question 4: 
```{r}
dac_benefit <- integrate(dac_demand_func, 0, q_mpc)$value
non_dac_benefit <- integrate(nondac_demand_func,0,q_mpc)$value

c <- (non_dac_benefit)-(dac_benefit)
```

The DAC and nonDAC consumers receive extremely disproportionate benefit from the current EV market. DAC consumers lose \$6,522,840,152, while non-DAC consumers receive \$4,493,211,327. Thus, there is a disparity of \$11,016,051,479 between the two groups. 

Question 5: 
```{r}
#a
q_star <- q_msc


optimal_tax <- external_cost(q_star)

#b
p_star <- agg_demand_func(q_star)

#g
revenue <- optimal_tax * q_star

#d
dac_benefit2 <- integrate(dac_demand_func, 0, q_msc)$value

change_dac <- dac_benefit2-dac_benefit

#c
non_dac_benefit2 <- integrate(nondac_demand_func,0,q_msc)$value
change_nondac <- non_dac_benefit2-non_dac_benefit

#e 
quant_diff <- q_mpc-q_msc

supplier_revenue0 <- q_mpc*50000

supplier_revenue1 <- q_msc*p_star

#e

revenue_diff <- supplier_revenue0-supplier_revenue1

#f

env_damage1 <- integrate(external_cost, 0, q_msc)$value

damage_diff <- env_damage0-env_damage1

```
optimal tax= $176,541.3 <br><br>
a. Amount of EVs produced/consumed from 65,485 to 9.34 <br><br>
b. price of EVs from \$50,000 to \$176,548.4 <br><br>
c. the overall welfare of nonDAC decreases by \$4,491,735,278 from \$4,493,211,327 to \$1,476,049 <br><br>
d. the overall welfare of DAC consumers increases by \$6,523,931,382 from -\$6,522,840,152 to \$1,091,230 <br><br>
e. The EV producers are producing 65,476.14 fewer cars, and losing $3,272,624,984.  <br><br>
f. Environmental damage is reduced by an equivalent of \$40,524,890,838,944 from \$40,524,891,663,463 to \$824,518.998. <br><br>
g. total tax revenue: $1,649,038






NOTES FROM OH: 
- need to add kink 
q = seq(o, 80000, 100)
demand_nonDAC = alpha_nd + beta_nd*q





